---
title: "Identifying network-derived biopsychosocial domains"
author: "Alexandria Andrayas"
date: "`r Sys.Date()`"
output:
  word_document:
    toc: true
#  html_document:
#    toc: true
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
```

# Load packages

```{r packages, message=FALSE, echo=F}
library(tidyverse)
library(labelled)
library(sticky)
library(mice)
library(EGAnet)
library(ggpubr)
library(dendextend)
library(gt)
library(gtsummary)
```

# Load and subset data and specify paths

```{r data, echo=F}
# Load dataset
load('//path/to/data/clean_data.rda')

# Subset dataset to those with data on pain at ages 26 AND 30
df <- alldf[!is.na(alldf$pain_status_26) & !is.na(alldf$pain_status_30),]

# Path to outputs
path_to_outputs <- "//path/to/outputs/"
```

# Variable labels

```{r labs, echo=F}
# List of long variable names
varlabs <- list(
  'aln'='Pregnancy identifier',
  'qlet'='Birth order (within pregnancy)',
  'sex'='Sex assigned at birth', 
  'ethnicity'='Ethnicity',
  'parent_sc_0' = 'Highest parental social class at birth',
  'pain_prob_7' = 'Pain problem in childhood (7y)',
  'parent_pain_12' = 'Parental pain (12y)',
  'sf12_sr_hlth_22'='SF-12: Self-rated health (22y)',
  'sf12_hlth_limt_mod_act_22'='SF-12: Health limits moderate activities (22y)',
  'sf12_ph_accomp_less_22'='SF-12: Freq. accomplished less due to physical health (22y)', 
  'sf12_emo_limt_wrk_act_22'='SF-12: Freq. work/activities limited by emotions (22y)',
  'sf12_calm_peace_22'='SF-12: Freq. felt calm and peaceful (22y)',
  'sf12_energy_22'='SF-12: Freq. had lot of energy (22y)',
  'sf12_limt_soc_act_22'='SF-12: Freq. health/emotions interfered with social activities (22y)',
  'wellbeing_sc_23'='Warwick-Edinburgh Mental Wellbeing Scale score (23y)', 
  'subj_happy_sc_23'='Subjective Happiness Scale score (23y)',
  'life_satis_sc_23'='Life Satisfaction Scale score (23y)',
  'meaning_life_presc_sc_23'='Meaning in Life Questionnaire: Presence score (23y)',
  'meaning_life_search_sc_23'='Meaning in Life Questionnaire: Search score (23y)',
  'basic_psych_needs_auton_sc_23'='BPNSS: Autonomy score (23y)', 
  'basic_psych_needs_compet_sc_23'='BPNSS: Competence score (23y)', 
  'basic_psych_needs_relat_sc_23'='BPNSS: Relatedness score (23y)',
  'gratitude_sc_23'='Gratitude Questionnaire score (23y)',
  'optimism_sc_23'='Life Orientation Test-Revised Optimism score (23y)',
  'smfq_sc_23'='Short Moods and Feelings Questionnaire score (23y)',
  'cisr_mild_depres_24'='CIS-R: Depression (24y)',
  'cisr_general_anxiety_24'='CIS-R: Generalised anxiety disorder (24y)',
  'scaared_total_25'='SCAARED: Total score (25y)', 
  'sapas_personality_dis_sc_24'='SAPAS: Total score (24y)',  
  'supps_neg_urg_24'='S-UPPS-P: Negative Urgency (24y)',
  'supps_pos_urg_24'='S-UPPS-P: Positive Urgency (24y)',
  'supps_lack_premed_24'='S-UPPS-P: Lack of Premeditation (24y)',
  'supps_lack_persev_24'='S-UPPS-P: Lack of Perseverance (24y)',
  'supps_sens_seek_24'='S-UPPS-P: Sensation Seeking (24y)',
  'sdq_prosocial_25'='SDQ: Prosocial behavior (25y)',
  'sdq_emotional_25'='SDQ: Emotional symptoms (25y)',
  'sdq_conduct_25'='SDQ: Conduct problems (25y)',
  'sdq_hyperact_25'='SDQ: Hyperactivity/inattention (25y)',
  'sdq_peer_25'='SDQ: Peer relationship problems (25y)',
  'aq_social_skill_sc_25'='AQ: Social Skills (25y)',
  'aq_attention_switch_sc_25'='AQ: Attention Switching (25y)',
  'aq_attention_detail_sc_25'='AQ: Attention to Detail (25y)',
  'aq_communication_sc_25'='AQ: Communication (25y)',
  'aq_imagination_sc_25'='AQ: Imagination (25y)',
  'ari_affect_react_sc_25'='ARI: Total Score (25y)',
  'atsrs_emo_support_sc_25'='ATSRS: Emotional support (25y)',
  'atsrs_prac_support_sc_25'='ATSRS: Instrumental support (25y)',
  'work_mem_24'='Working memory: N-back d prime (24y)',
  'resp_inhib_24'='Response inhibition: Stop-Signal reaction time, ms (24y)', 
  'screen_time_22'='Hours per day spent using screens on average (22y)',
  'outdoor_time_22'='Hours per day spent outdoors on average (22y)',
  'actv_jrnys_22'='Regular walking/cycling journeys (22y)',
  'vigact_freq_22'='Freq. taking part in strenuous/vigorous activity (22y)',
  'eat_conscious_25'='Conscious of what they are eating (25y)',
  'n_hrs_sleep_25'='Number of hours sleeps in 24 hours (25y)', 
  'enough_sleep_25'='Frequency gets enough sleep (25y)', 
  'daytime_tired_25' = 'Problem with sleepiness during day time activities (25y)',
  'smk_vape_cannabis_24'='Nicotine or cannabis use (24y)',
  'bing_drink_24'='Binge drinking (24y)',
  'n_illict_drugs_24'='Number of illicit drugs ever used (24y)', 
  'antisocialb_22'='Anti-social behaviour (22y)',
  'n_siblings_23'='Number of siblings (23y)',
  'n_friends_24'='Number of close friends (24y)',
  'freq_see_parents_25'='Frequency sees parents (25y)',
  'socmed_freq_24'='Social media use frequency (24y)',
  'parent_25'='Is a parent (25y)',
  'partner_25'='Has a partner (25y)',
  'lives_alone_25'='Lives alone (25y)',
  'volunteer_22'='Doing volunteer work (22y)',
  'inedu_22'='In part-/full-time education (22y)',
  'income_25'='Take-home pay each month (25y)',
  'job_shift_nights_25'='Has job that involves shift work or night shifts (25y)',
  'n_jobs_school_25' = 'Number of jobs had since leaving school (25y)',
  'financ_prob_25'='Had big financial problems past year (25y)',
  'bullied_23'='Bullied, past 6 months (23y)',
  'feltlov_grwup_23'='Felt loved growing up (23y)',
  'feltlov_relat_23'='Felt loved by a partner since 16 (23y)',
  'relationship_abuse_23' = 'Relationship abuse since 16 (23y)',
  'childh_maltreat_23' = 'Childhood maltreatment growing up (23y)',
  'serious_accident_fire_23'='Ever been in a serious accident or fire (23y)',
  'death_somclos_23'='Unexpected death of someone close (23y)',
  'bad_exps_24'='Bad experience in past year (24y)',
  'selfharm_24'='Self-harm history (24y)',
  'lean_mass_ind_24'='Lean mass index (24y)',
  'bmi_24'='Body Mass Index (24y)',
  'heartrate_24'='Heart Rate average, bpm (24y)',
  'grip_strength_24'='Maximum hand grip strength (24y)',
  'log_crp_24'='C-Reactive Protein, mg/l log-transformed (24y)',
  'il6_24'='Interleukin-6,NPX values log2 scale (24y)',
  'nlr_24' = 'Neutrophil-to-Lymphocyte Ratio (24y)',
  'wbc_24' = 'White blood cell count 10^9/L (24y)',
  'log_insulin_24' = 'Insulin uU/mL log-transformed (24y)',
  'log_triglycerides_24'='Triglycerides mmol/L log-transformed (24y)',
  'aches_sickness_25' = 'Regular headaches, stomach-aches or sickness (25y)',
  'gp_visits_24'='GP visits about own health, past year (24y)',
  'longst_ill_disab_24'='Long-standing illness/disability/infirmity (24y)', 
  'urbrur_24'='Urban/rural indicator (24y)',
  'imdq_24'='IMD Neighbourhood deprivation, quintiles (24y)',
  'townsendq_24'='Townsend deprivation score, quintiles (24y)',
  'pain_status_18' = 'Pain status (18y)',
  'pain_status_26'='Pain status (26y)',
  'pain_status_30'='Pain status (30y)'
  )
#names(varlabs)[!names(varlabs) %in% colnames(df)]
#colnames(df)[!colnames(df) %in% names(varlabs)]
```

# Tidy and check dataset 

```{r clean, echo=F}
# Subset dataset to only include IDs, demographics, multidomain exposure items and pain outcomes
df <- df[,names(varlabs)]

# Exclude IDs, confounders and outcomes
non_exp_vars <- c("aln", "qlet",
                  'sex','ethnicity','parent_sc_0',
                  'pain_prob_7','parent_pain_12', 
                  'pain_status_18', 'pain_status_26', 'pain_status_30')

# Covariates
covariates <- c('sex','ethnicity','parent_sc_0', 'pain_prob_7','parent_pain_12')

# Number of exposure items initially included in EGA
analy_vars <- colnames(df)[!colnames(df) %in% non_exp_vars]
#length(analy_vars) #92

# Recode binary variables from factor to numeric
numeric_vars <- df %>% select(-all_of(non_exp_vars)) %>% select(where(~ is.numeric(.x))) %>% names()

# Check variable types
categorical_vars <- df %>%
  select(-all_of(non_exp_vars)) %>%
  select(where(~ is.factor(.x) && nlevels(.x) > 2)) %>%
  names()

binary_vars <- df %>%
  select(-all_of(non_exp_vars)) %>%
  select(where(~ is.factor(.x) && nlevels(.x) == 2)) %>%
  names()

ordered_vars <- df %>%
  select(-all_of(non_exp_vars)) %>%
  select(where(~ is.ordered(.x))) %>%
  names()

#length(ordered_vars)
#table(categorical_vars %in% ordered_vars)
#length(numeric_vars)+length(categorical_vars)+length(binary_vars)
#ncol(df)-length(non_exp_vars)

#!!!
#df <- df %>% mutate(across(all_of(binary_vars), ~ {as.integer(f) - 1}))

# Assign labels
var_label(df) <- varlabs[colnames(df)]

# Persist label attributes
df <- sticky_all(df)
```

# Missingness proportions

```{r missingness}
# Number of complete cases
nrow(df[complete.cases(df[,analy_vars]),])
#393
nrow(df[complete.cases(df[,c(analy_vars,covariates)]),])
#286

# Item-level missingness
miss_tab <- data.frame(
  var = c(analy_vars,covariates),
  n_missing = colSums(is.na(df[, c(analy_vars,covariates)])),
  prop_missing = colMeans(is.na(df[, c(analy_vars,covariates)]))
) |>
  dplyr::arrange(desc(prop_missing))

miss_tab

# Summary range
range(miss_tab$prop_missing[!miss_tab$var %in% 'sex'])
median(miss_tab$prop_missing)
quantile(miss_tab$prop_missing[!miss_tab$var %in% 'sex'], c(.25, .75))
head(miss_tab, 10)
```

# Load imputed data

```{r load-imp-dat}
# Load imputed data
load('//path/to/data/mult_pain_imp_all.rda')
```

# Run EGAs

```{r imp-egas-non-redundant, out.width='100%', warning=F}
# Load vector of identified redundancies
load(paste0(path_to_outputs,'redundant_vars.rda'))
nonredund_vars <- setdiff(analy_vars, redundant_vars)

# Function to run EGA on datasets
get_imp_ega <- function(imp_data, variables) {
  n_imputations <- imp_data$m
  ega_list <- vector('list', n_imputations)
  for(i in 1:n_imputations) {
    complete_data <- complete(imp_data, i)[,variables]
    set.seed(5402)
    ega_list[[i]] <- EGA(data=complete_data,
                         model='glasso',
                         algorithm='walktrap',
                         plot.EGA=FALSE)
  }
  return(ega_list)
}

# Run EGA for each imputed dataset removing redundant
imp_egas <- get_imp_ega(imp_all, nonredund_vars)

# View EGA plots - only first four as too many too show
comp_ega_plts <- compare.EGA.plots(input.list=(imp_egas[c(1:4)]), columns=2, plot.all=F, label.size=1.5, vsize=2)
ggarrange(plotlist = comp_ega_plts$individual, ncol=2, nrow=2, 
          common.legend = TRUE, legend = "bottom")
```

# Identify communities

## Co-occurrence matrix

Shows how often out of m imputations each pair of items cluster together.

```{r co-occur, out.width='100%'}
# Function to create co-occurrence matrix
get_co_occur <- function(impdat, var_names) {
  m <- length(impdat)
  wc_list <- lapply(impdat, function(ega) ega$wc[var_names])
  
  mats <- lapply(wc_list, function(wc) {
    mat <- outer(wc, wc, `==`)
    mat[is.na(mat)] <- FALSE
    mat
  })
  
  C <- Reduce(`+`, mats)
  dimnames(C) <- list(var_names, var_names)
  diag(C) <- m
  
  C
}

co_occur <- get_co_occur(imp_egas, nonredund_vars)

# Plot co-occurrence matrix
melted_co_occur <- as.data.frame(as.table(co_occur))

plt_mat <- function(melt_obj, fill_lab, fill_val){
  ggplot(melt_obj, aes(x=Var1, y=Var2, fill=.data[[fill_val]])) +
    geom_tile() +
    scale_fill_gradient(low='white', high='steelblue') +
    labs(x='', y='', fill=fill_lab) +
    theme_minimal() +
    theme(axis.text.x=element_text(angle=45, hjust=1),
          axis.text.y=element_text(size=5),
          legend.position='bottom')
}

co_occur_plt <- plt_mat(melted_co_occur, 'Co-occurrence', 'Freq')

ggsave(plot=co_occur_plt, filename=paste0(path_to_outputs,"co_occur_plt.png"), width=14, height=9, dpi=350)
```

## Dendrogram

Then used the co-occurance matrix to do hierarchical clustering and identify clusters. We then specify the number of clusters to get item assignments (based on mean number of dimensions across imputations).

```{r hclust, out.width='100%'}
# Convert to distance matrix (1 - proportion of times clustered together)
co_occur_prop <- co_occur / length(imp_egas)
dist_mat <- as.dist(1 - co_occur_prop)

# Hierarchical clustering
hc <- hclust(dist_mat, method='average')  # or 'complete'

# Number of dimensions identified in each imputation
n_dims <- sapply(imp_egas, function(x) x$n.dim)
table(n_dims)
k_mode <- as.integer(names(sort(table(n_dims), decreasing=TRUE)[1]))

# Plot dendrogram
dhc <- as.dendrogram(hc)
dhc <- dhc %>%
  color_branches(k=k_mode) %>%
  color_labels(k=k_mode)  %>%
  set("labels", varlabs[labels(dhc)]) %>%
  set("labels_cex", 0.5) 

png(paste0(path_to_outputs,'dendrogram.png'), width=9, height=6, units='in', res=350)
par(mar=c(10, 4, 1, 0))
plot(dhc, main=NULL, cex.axis=0.7, dLeaf=0.02)
dev.off()
```

# Cluster assignments

```{r imp-cluster-assign}
# Get cluster assignments
clusters_imp <- cutree(hc, k=k_mode)
cluster_imp_items <- split(names(clusters_imp), clusters_imp)
lengths(cluster_imp_items)

# Long labels
clusters_imp_longlabs <- clusters_imp
names(clusters_imp_longlabs) <- varlabs[names(clusters_imp_longlabs)] 

# Print figure label footnote
#cat(paste(names(clusters_imp), "=", names(clusters_imp_longlabs)), sep = "; ")

# Domain names
cluslabs <- list(
  `clus1` = "Functional-behavioural health difficulties",
  `clus2` = "Positive wellbeing",
  `clus3` = "Distress and adversity",
  `clus4` = "Social communication and peer problems",
  `clus5` = "Interpersonal support and security",
  `clus6` = "Activity engagement and resources",
  `clus7` = "Bio-health indicators"
)

# Create data frame to display data-driven domains
clusters_df <- data.frame(
  `n`=rep(1:length(cluslabs), times=lengths(cluster_imp_items)),
  `domain`=rep(unname(unlist(cluslabs)), times=lengths(cluster_imp_items)), 
  `items`=names(clusters_imp_longlabs[order(clusters_imp_longlabs)]),
  `label`=names(clusters_imp[order(clusters_imp)])
  )

# Generate gt table
clusters_tab <- clusters_df %>%
  gt() %>%
  cols_label(
    `n`='Number',
    `domain`='Network-derived domain',
    `items`='Items',
    `label`='Label'
  ) %>%
  tab_style(style=cell_text(weight='bold'), 
            locations=cells_column_labels()) %>%
  tab_style(style=cell_text(whitespace='pre-wrap'),
            locations=cells_body(columns=c(items,label)))

clusters_tab %>% gtsave(filename=paste0(path_to_outputs,"network_domains_tab.docx"))
```

## Average EGA plot

```{r imp-avg-ega, out.width='100%'}
# Get average network
imp_networks_list <- lapply(imp_egas, function(ega) ega$network)
imp_networks <- do.call(cbind, imp_networks_list)
imp_networks <- array(imp_networks, dim=c(dim(imp_networks_list[[1]]), length(imp_networks_list)))

avg_imp_netw <- apply(imp_networks, c(1, 2), mean, na.rm=TRUE)
rownames(avg_imp_netw) <- names(clusters_imp)
colnames(avg_imp_netw) <- names(clusters_imp)

# Build EGAnet object
ega_avg <- list(
  network=avg_imp_netw,
  wc=clusters_imp
)
class(ega_avg) <- "EGA"

# Domain labels in the order used by the plot
domain_labs <- unname(cluslabs)

# colours in the same order
domain_cols <- c("#56B4E9", "#F0E442", "#009E73", "#D55E00","#CC79A7", "#0072B2", "#E69F00")
domain_cols <- domain_cols[seq_along(cluslabs)]
#palette.colors(palette = "Okabe-Ito") #colour-blind friendly

# Plot
ega_avg_plt <- plot(
  ega_avg,
  label.size = 3,
  vsize = 6,
  color.palette = unname(domain_cols)
) +
  scale_colour_identity(
    name = "Domain:  ",
    breaks = unname(domain_cols),
    labels = domain_labs,
    guide = "legend"
  ) +
  guides(colour = guide_legend(ncol = 2, override.aes = list(size = 5))
  ) +
  theme(
    legend.position = "bottom",
    legend.title = element_text(size = 8),
    legend.text = element_text(size = 8),
    legend.key.size = unit(2, "mm"),
    legend.spacing.y = unit(1, "mm")
  )

ega_avg_plt

ggsave(plot=ega_avg_plt, filename=paste0(path_to_outputs,"avg_ega_plt.png"), width=174, height=194, units="mm", dpi=350)
```

### Label key table

```{r labs, echo=F}
label_key <- data.frame('item' = names(unlist(varlabs[nonredund_vars])), 
                        'label' = unlist(varlabs[nonredund_vars]))

label_key <- label_key[order(label_key$item),]

label_key %>%
  gt() %>%
  cols_label(item = "Short label", label = "Long label") %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels()
  ) %>% gtsave(filename=paste0(path_to_outputs,"label_key.docx"))
```

### 3D plot

```{r imp-3d-plt, echo=F, out.width='100%'}
#!!! blocked out for word doc !!!

#library(igraph)
#library(plotly)

# Force weights to be non-negative for the layout
#W <- abs(avg_imp_netw)
#diag(W) <- 0

#g <- graph_from_adjacency_matrix(W, mode="undirected", weighted=TRUE, diag=FALSE)

#set.seed(1)
#var_coord <- layout_with_fr(g, dim=3, weights=E(g)$weight)
#rownames(var_coord) <- colnames(W)

#plot_ly(
#  x=var_coord[,1], y=var_coord[,2], z=var_coord[,3],
#  type="scatter3d", mode="markers+text",
#  text=names(clusters_imp), textposition="top center",
#  color=factor(clusters_imp), #colour by communities
#  marker=list(size=4)
#  ) %>%
#  layout(scene=list(
#    xaxis=list(title="Dim 1"),
#    yaxis=list(title="Dim 2"),
#    zaxis=list(title="Dim 3")
#  ))
```

## Average network loadings

```{r imp-avg-netw-loadings, warning=F, message=F, out.width='100%'}
# Get network loadings from average EGA objects (sparse set to 0)
avg_imp_nwloads <- net.loads(ega_avg, minimum=0.1) #defaults to 0.1

# Print average standardised loadings
avg_imp_nwloads$std %>% 
  as.data.frame() %>%
  tibble::rownames_to_column(var = "item") %>%
  tibble::as_tibble() %>%
  dplyr::rename_with(~ unlist(cluslabs), -item) %>%
  gt() %>%
  fmt_number(decimals = 3) %>%
  gtsave(filename=paste0(path_to_outputs,"network_loadings_tab.docx"))

#Plot standardised loadings
melted_loads <- as.data.frame(as.table(avg_imp_nwloads$std))
ggplot(melted_loads, aes(x=Var2, y=Var1, fill=Freq)) +
  geom_tile() +
  #geom_text(aes(label=sprintf("%.2f", value)), size=2) +
  scale_x_discrete(breaks=1:length(cluslabs),
                     labels=paste0('\n', cluslabs)) +
  scale_fill_gradient2(low='coral', mid='white', high='steelblue') +
  labs(x='', y='', fill='Network loading') +
  theme_minimal() +
  theme(axis.text.x=element_text(size=5, face="bold"),
        axis.text.y=element_text(hjust=1, size=5),
        legend.position='right')
```

## Network scores

```{r imp-netw-sc, warning=F, message=F}
# Get list of networks
imp_networks_list <- lapply(imp_egas, function(x) x[['network']])

# Function to get run net.scores
get_imp_netw_sc <- function(imp_data, variables) {
  n_imputations <- imp_data$m
  netw_sc_list <- vector('list', n_imputations)
  for(i in 1:n_imputations) {
    compl_data <- complete(imp_data, i)[, variables]
    netw <- imp_networks_list[[i]]
    netw_sc_list[[i]] <- suppressMessages(
      net.scores(data=compl_data, 
                 A=netw, 
                 wc=clusters_imp,
                 loading.method="revised")
      )
  }
  return(netw_sc_list)
}

# Run net.scores for each imputed dataset
imp_netw_scores <- get_imp_netw_sc(imp_all, nonredund_vars)
##Warning: Several variables were coerced to numeric values. These variables were changed to numeric values

# Z-standardise scores and add column names
imp_netw_z_scs <- lapply(imp_netw_scores, function(x) {
  scs <- as.data.frame(x$scores$std.scores)
  colnames(scs) <- paste0("clus", seq_along(cluster_imp_items))
  scs %>% mutate(across(everything(), ~ as.numeric(scale(.x))))
})
save(imp_netw_z_scs, file="//path/to/data/imp_netw_z_scs.rda")
```

### Average correlations between scores

```{r imp-avg-corr, out.width='100%'}
# Get correlations between network scores for each imputation
imp_netwsc_corrs_list <- lapply(imp_netw_z_scs, auto.correlate)

# Fisher z-transform, average, then back-transform
z_corrs_list <- lapply(imp_netwsc_corrs_list, function(R) {
  R <- as.matrix(R)
  diag(R) <- NA  # avoid atanh(1) = Inf on the diagonal
  atanh(R)
})

z_array <- simplify2array(z_corrs_list)

avg_z_corrs <- apply(z_array, c(1, 2), mean, na.rm = TRUE)

avg_imp_netwsc_corrs <- tanh(avg_z_corrs)
diag(avg_imp_netwsc_corrs) <- 1

rownames(avg_imp_netwsc_corrs) <- cluslabs
colnames(avg_imp_netwsc_corrs) <- cluslabs

# Plot correlations
long_imp_nws_corr <-as.data.frame(as.table(avg_imp_netwsc_corrs))

avg_netwsc_corrs <- ggplot(long_imp_nws_corr, aes(x=Var2, y=Var1)) + 
  geom_raster(aes(fill=Freq)) + 
  geom_text(aes(label=sprintf("%.2f", Freq)), size=5) +
  scale_fill_gradient2(low="#5D3A9B", mid="#FFFFFF", high="#E69F00") + 
  theme(axis.title=element_blank(),
        axis.text.x=element_text(size=15, angle=45, hjust=1),
        axis.text.y=element_text(size=15),
        legend.title=element_blank(),
        legend.text=element_text(size=12))

ggsave(plot=avg_netwsc_corrs, filename=paste0(path_to_outputs,"avg_netwsc_corrs.png"), width=14, height=12, dpi=350)
```

### Density plots

```{r imp-netw-sc-plts, echo=F, out.width='100%'}
long_netw_z_scs <- bind_rows(
  lapply(seq_along(imp_netw_z_scs), function(i) {
    as.data.frame(imp_netw_z_scs[[i]]) %>%
      mutate(impn=i)
  })
) %>%
  pivot_longer(
    cols=starts_with("clus"),
    names_to="cluster",
    values_to="score"
  )

hists <- lapply(names(cluslabs), function(cl){
  ggplot(filter(long_netw_z_scs, cluster == cl),
         aes(x=score, colour=impn, group=impn)) +
    geom_density(linewidth=0.2, na.rm=TRUE) +
    scale_colour_gradient(low="#5D3A9B", high="#E69F00", name="Imputation number") +
    theme_minimal() +
    theme(text=element_text(size=8)) +
    labs(x=cluslabs[[cl]], y="Density")
})

hist_plt <- ggarrange(plotlist = hists, ncol=2, nrow=4,
                      common.legend = TRUE,
                      legend = "bottom")
hist_plt

#ggsave(plot=hist_plt, filename=paste0(path_to_outputs,"hist_plt.png"), width=8, height=10, dpi=350)

#!! look at responses vs network scores to get a feel of what they represent
```

# Patterns of missingness in included variables

```{r desc-stats-clus1, message=F, warning=F, echo=F}
#!blocked out as doesn't show in markdown
#library(naniar)
#fix_upset_labs <- function(x) {#function to remove NAs from upset plot
#  if (!is.null(x$label) && is.character(x$label)) {
#    x$label <- sub("_NA$", "", x$label)
#  }
#  if (!is.null(x$children)) x$children <- lapply(x$children, fix_upset_labs)
#  if (!is.null(x$grobs))    x$grobs    <- lapply(x$grobs,    fix_upset_labs)
#  if (!is.null(x$grob))     x$grob     <- fix_upset_labs(x$grob)
#  x
#}

#png(paste0(path_to_outputs,"upset_missing_plt.png"), width = 9, height = 6, units = "in", res = 350)
#upset_ana_samp <- gg_miss_upset(df[,nonredund_vars], nsets = 20, point.size = 1.4, number.angles = 0, text.scale = 0.7)
#upset_ana_samp$Matrix   <- fix_upset_labs(upset_ana_samp$Matrix)
#upset_ana_samp
#dev.off()
#!
```

# Descriptive statistics per cluster

```{r desc-stats-domains, message=F, warning=F, echo=F}
make_desc_tab <- function(dom_items) {
  
  problem_vars <- c(
    "sapas_personality_dis_sc_24",
    "sdq_conduct_25",
    "sdq_peer_25"
    )

  cont_vars <- intersect(problem_vars, dom_items)
  
  type_arg <- if (length(cont_vars) > 0) {
    list(all_of(cont_vars) ~ "continuous")
  } else {
    NULL
  }
  
  tbl_summary(
    df[, dom_items, drop = FALSE],
    missing = "no",
    type = type_arg
  ) %>%
    italicize_levels() %>% 
    add_n(statistic = "{N_miss} ({p_miss}%)") %>%
    modify_header(n = "**Missing**")
}

desc_tab_list <- lapply(cluster_imp_items, make_desc_tab)
desc_tab_by_domain <- tbl_stack(desc_tab_list, group_header = unlist(cluslabs))

desc_tab_by_domain %>% 
  as_gt() %>% 
  gtsave(filename=paste0(path_to_outputs,"desc_stats_by_domain.docx"))
```
