---
title: "Tables and figures"
author: "Alexandria Andrayas"
#output: html_document
output: word_document
date: "`r Sys.Date()`"
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(haven)
library(labelled)
library(sticky)
library(tidyverse)
library(gt)
library(gtsummary)
library(broom)
library(biostat3)
library(ggpubr)
library(ggcorrplot)
library(Gmisc)
library(grid)
library(glue)

path_to_data <- "//path/to/data/"
path_to_outputs <- "//path/to/outputs/"
```


# SF-36 ITEMS TABLE

```{r sf36-items, echo=FALSE}
sf36_df <- data.frame(
  `Selfcare` = c(
    "Doing moderate activities (e.g., moving a table, pushing a vacuum cleaner, bowling, or playing golf)",
    "Lifting or carrying groceries",
    "Climbing one flight of stairs",
    "Bending, kneeling, or stooping",
    "Walking one hundred metres",
    "Walking half a mile",
    "Bathing or dressing"
  ),
  `Social` = c(
    "Cut down on amount of time spent on work or other activities due to emotional problems",
    "Accomplished less than would like due to emotional problems",
    "Did work or activities less carefully than usual due to emotional problems",
    "Time physical or emotional problems interfered with social activities",
    "Extent of interference with normal social activities with family, friends, neighbours, or groups",
    "", ""
  ),
  `Work` = c(
    "Cut down on amount of time spent on work or other activities due to physical health",
    "Accomplished less than would like due to physical health",
    "Limited in kind of work or other activities due to physical health",
    "Difficulty performing work or other activities (e.g., it took extra effort)",
    "", "", ""
  ),
  stringsAsFactors = FALSE
)

sf36_df %>%
  gt() %>%
  cols_label(
    `Selfcare` = "Daily domain",
    `Social` = "Social domain",
    `Work` = "Work domain"
  ) %>%
  tab_style(style = cell_text(weight = "bold"), 
            locations = cells_column_labels())
```


# SOCIAL SUPPORT ITEMS TABLE

```{r supp-items, echo=FALSE}
supp_df <- data.frame(
  `Emotional` = c(
    'I have someone who understands my problems',
    'I have someone who will listen to me when I need to talk',
    'I feel there are people I can talk to if I am upset',
    'I have someone to talk with when I have a bad day', 
    'I have someone I trust to talk with about my problems',
    'I have someone I trust to talk with about my feelings',
    'I can get helpful advice from others when dealing with a problem',
    'I have someone to turn to for suggestions about how to deal with a problem'
  ),
  `Practical` = c(
    'Someone is around to make my meals if I am unable to do it myself',
    'I have someone to take me shopping if I need it',
    'I have someone to help me if I am sick in bed',
    'I have someone to pick up medicine for me if I need it',
    'I have someone to take me to the doctor if I need it',
    'There is someone around to help me if I need it',
    'I can find someone to drive me places if I need it',
    'I can get help cleaning up around my home if I need it'
  ),
  stringsAsFactors = FALSE
)

supp_df %>%
  gt() %>%
  cols_label(
    `Emotional` = "Emotional support",
    `Practical` = "Practical support"
  ) %>%
  tab_style(style = cell_text(weight = "bold"), 
            locations = cells_column_labels())
```

# G-COMPUTATION EFFECTS DESCRIPTION TABLE

```{r gform-ests, echo=FALSE}
g_med_effs_df <- data.frame(
  `Effect` = c(
    "Total Causal Effect (TCE)",
    "Natural Direct Effect (NDE)",
    "Natural Indirect Effect (NIE)",
    "Proportion Mediated (PM)",
    "Controlled Direct Effect (CDE)"
  ),
  `Description` = c(
    "Difference between potential outc_labs if all experienced high (X=1) vs. low (X=0) pain impact where support varies naturally.",
    "Difference between potential outc_labs if all had high pain impact but support fixed at level under low pain impact vs. all had low pain impact.",
    "Difference between TCE and NDE, capturing effect via support.",
    "Proportion of the total effect of early pain impact on low pain impact explained by support (NIE / TCE).",
    "Difference between potential outc_labs for high vs low pain impact, if support is fixed to high (m=1) for everyone in this case."
  )#,
  #`Formula` = c(
  #  "log{E[Y{X=1,M(X=1)}] / (1-E[Y{X=1,M(X=1)}])} - log{E[Y{X=0,M(X=0)}] / (1-E[Y{X=0,M(X=0)}])}",
  #  "log{E[Y{X=1,M(X=0)}] / (1-E[Y{X=1,M(X=0)}])} - log{E[Y{X=0,M(X=0)}] / (1-E[Y{X=0,M(X=0)}])}",
  #  "TCE - NDE",
  #  "NIE / TCE",
  #  "log(E{Y(X=1,M=m)} / [1-E{Y(X=1,M=m)}]) - log(E{Y(X=0,M=m)} / [1-E{Y(X=0,M=m)}])"
  #  )
)

g_med_effs_df %>%
  gt() %>%
  cols_label(
    `Effect` = "Effect Type",
    `Description` = "Explanation"#,
    #`Formula` = "Formula"
  ) %>%
  #cols_width(everything()~px(400)) %>%
  tab_style(style = cell_text(weight = "bold"), 
            locations = cells_column_labels())
```


```{r load, echo=FALSE}
# Read in data and remove attributes
alldf <- read_dta(paste0(path_to_data,'data_irt_all.dta'))
alldf <- data.frame(to_factor(alldf, sort_levels='auto'))
alldf <- remove_attributes(alldf, 'format.stata')

# Define measures
exp_labs <- c('selfc_spl_18','social_spl_18','work_spl_18')
intc_labs <- c('mfq_cutoff_21','gad_cutoff_21')
med_labs <- c('social_integration_sc_grp_25',
              'emo_supp_sc_grp_25',
              'prac_supp_sc_grp_25',
              'covid_inpers_cont_adult_grp_28',
              'covid4_dist_cont_adult_grp_28')
outc_labs <- c('daily_spl_30', 'social_spl_30', 'work_spl_30')

# Baseline confounders
baseconf <- c('ethnicity', 'm_pregsmk', 'parent_sc_0', 'm_homown_0', 'parent_mhp_1')

# Long labels
long_labs <- list('sex' = 'Sex assigned at birth, female', 
                  'ethnicity' = 'Ethnicity, white',
                  'm_pregsmk' = 'Mother smoked in pregnancy (0y)', 
                  'parent_sc_0' = 'Highest parental social class (0y)', 
                  'm_homown_0' = 'Maternal home ownership (0y), rented', 
                  'parent_mhp_1' = 'Parental mental health condition (1y)',
                  'pain_1day_mnth_18' = 'Pain >= 1 day in past month (18y)', 
                  'pain_more3mnths_18' = 'Pain >= 3 months (18y)',
                  'pain_1day_mnth_30' = 'Pain >= 1 day in past month (30y)', 
                  'pain_more3mnths_30' = 'Pain >= 3 months (30y)',
                  'selfc_spl_18' = 'Health limits daily activities (18y)',
                  'social_spl_18' = 'Health limits social activities (18y)',
                  'work_spl_18' = 'Health limits work (18y)',
                  'mfq_cutoff_21' = 'Higher depressive symptoms (21y)',
                  'gad_cutoff_21' = 'Higher anxiety symptoms (21y)',
                  'social_integration_sc_grp_25' = 'Wider social network (25y)',
                  'emo_supp_sc_grp_25' = 'Higher emotional support (25y)',
                  'prac_supp_sc_grp_25' = 'Higher practical support (25y)',
                  'covid_inpers_cont_adult_grp_28' = 'In-person COVID contact (28y)',
                  'covid4_dist_cont_adult_grp_28' = 'Distant COVID contact (28y)',
                  'daily_spl_30' = 'Pain impacts daily activities (30y)', 
                  'social_spl_30' = 'Pain impacts social activities (30y)', 
                  'work_spl_30' = 'Pain impacts work activities (30y)'
)

# Assign labels
var_label(alldf) <- long_labs

# Persist labels
alldf <- sticky_all(alldf)

# Create subsetted dataset limiting to those with pain at 18
df_wpain <- alldf[alldf$pain_1day_mnth_18 %in% 1,]
```


# FLOWCHART

```{r flowchart-func, echo=FALSE}
# Helper for comma-formatted counts
nfmt <- function(x) format(x, big.mark = ",", scientific = FALSE)

# Function to produce boxes
make_box <- function(header, body = NULL, x, y,
                     width = unit(0.28, "npc"),
                     fill = "#F7F7F7",
                     cex = 0.75) {
  
  if (is.null(body)) {
    boxGrob(
      label = header,
      x = unit(x, "npc"),
      y = unit(y, "npc"),
      width = width,
      txt_gp = gpar(cex = cex),
      box_gp = gpar(fill = fill, col = "grey30")
    )
  } else {
    boxHeaderGrob(
      header = header,
      body = body,
      x = unit(x, "npc"),
      y = unit(y, "npc"),
      width = width,
      header_gp = gpar(fontface = "bold", cex = cex),
      body_gp = gpar(cex = cex * 0.9),
      box_gp = gpar(fill = fill, col = "grey30")
    )
  }
}

# Function to produce flowchart
draw_attrition_flowchart <- function() {
  
  # Counts
  n_initial <- nrow(alldf)
  n_baseconf <- nrow(alldf[complete.cases(alldf[,baseconf]),])
  n_exp <- nrow(alldf[complete.cases(alldf[,c(baseconf,exp_labs)]),])
  n_exp_intc <- nrow(alldf[complete.cases(alldf[,c(baseconf,exp_labs,intc_labs)]),])
  n_exp_med <- nrow(alldf[complete.cases(alldf[,c(baseconf,exp_labs,med_labs)]),])
  n_exp_intc_med <- nrow(alldf[complete.cases(alldf[,c(baseconf,exp_labs,intc_labs,med_labs)]),])
  n_exp_outc <- nrow(alldf[complete.cases(alldf[,c(baseconf,exp_labs,outc_labs)]),])
  n_exp_med_outc <- nrow(alldf[complete.cases(alldf[,c(baseconf,exp_labs,med_labs,outc_labs)]),])
  n_full <- nrow(alldf[complete.cases(alldf[,c(baseconf,exp_labs,intc_labs,med_labs,outc_labs)]),])
  
  n_baseconf_prop <- round(n_baseconf/nrow(alldf)*100,0)
  n_exp_prop <- round(n_exp/nrow(alldf)*100,0)
  n_exp_intc_prop <- round(n_exp_intc/nrow(alldf)*100,0)
  n_exp_med_prop <- round(n_exp_med/nrow(alldf)*100,0)
  n_exp_intc_med_prop <- round(n_exp_intc_med/nrow(alldf)*100,0)
  n_exp_outc_prop <- round(n_exp_outc/nrow(alldf)*100,0)
  n_exp_med_outc_prop <- round(n_exp_med_outc/nrow(alldf)*100,0)
  n_full_prop <- round(n_full/nrow(alldf)*100,0)
  
  grid.newpage()
  
  b_initial <- make_box(
    header = glue("Eligble sample who provided pain data (age 18)\nN = {nfmt(n_initial)}"),
    x = 0.50, y = 0.94,
    width = unit(0.34, "npc")#,
    #fill = "#E8F0FF"
  )
  
  b_base <- make_box(
    header = glue("Complete baseline confounders\nN = {nfmt(n_baseconf)} ({n_baseconf_prop}%)"),
    x = 0.50, y = 0.82,
    width = unit(0.34, "npc")#,
    #fill = "#E8F0FF"
  )
  
  b_hlthlim <- make_box(
    header = glue("+ Complete health limitations (age 18)\nN = {nfmt(n_exp)} ({n_exp_prop}%)"),
    x = 0.50, y = 0.66,
    width = unit(0.34, "npc")#,
    #fill = "#E6F4EA"
  )
  
  b_mh <- make_box(
    header = glue("+ Complete mental health (age 21)\nN = {nfmt(n_exp_intc)} ({n_exp_intc_prop}%)"),
    x = 0.18, y = 0.44,
    width = unit(0.27, "npc")#,
    #fill = "#FFF4E6"
  )
  
  b_social <- make_box(
    header = glue("+ Complete social network/support/contact (ages 23-28)\nN = {nfmt(n_exp_med)} ({n_exp_med_prop}%)"),
    x = 0.50, y = 0.44,
    width = unit(0.35, "npc")#,
    #fill = "#FFF4E6"
  )
  
  b_later <- make_box(
    header = glue("+ Complete pain impact (age 30)\nN = {nfmt(n_exp_outc)} ({n_exp_outc_prop}%)"),
    x = 0.82, y = 0.44,
    width = unit(0.27, "npc")#,
    #fill = "#FFF4E6"
  )
  
  b_mh_social <- make_box(
    header = glue("Complete mental health + social network/support/contact\nN = {nfmt(n_exp_intc_med)} ({n_exp_intc_med_prop}%)"),
    x = 0.32, y = 0.22,
    width = unit(0.35, "npc")#,
    #fill = "#F2E8FF"
  )
  
  b_social_pimp <- make_box(
    header = glue("Complete social network/support/contact + pain impact\nN = {nfmt(n_exp_med_outc)} ({n_exp_med_outc_prop}%)"),
    x = 0.68, y = 0.22,
    width = unit(0.35, "npc")#,
    #fill = "#F2E8FF"
  )
  
  b_final <- make_box(
    header = glue("Full complete-records sample\nN = {nfmt(n_full)} ({n_full_prop}%)"),
    x = 0.50, y = 0.07,
    width = unit(0.44, "npc")#,
    #fill = "#FDECEC"
  )
  
  boxes <- list(
    b_initial, b_base, b_hlthlim,
    b_mh, b_social, b_later,
    b_mh_social, b_social_pimp,
    b_final
  )
  
  lapply(boxes, grid.draw)
  
  # Connections
  grid.draw(connectGrob(b_initial, b_base, type = "vert"))
  grid.draw(connectGrob(b_base, b_hlthlim, type = "vert"))
  
  grid.draw(connectGrob(b_hlthlim, b_mh, type = "N"))
  grid.draw(connectGrob(b_hlthlim, b_social, type = "vert"))
  grid.draw(connectGrob(b_hlthlim, b_later, type = "N"))
  
  grid.draw(connectGrob(b_mh, b_mh_social, type = "N"))
  grid.draw(connectGrob(b_social, b_mh_social, type = "N"))
  
  grid.draw(connectGrob(b_social, b_social_pimp, type = "N"))
  grid.draw(connectGrob(b_later, b_social_pimp, type = "N"))
  
  grid.draw(connectGrob(b_mh_social, b_final, type = "N"))
  grid.draw(connectGrob(b_social_pimp, b_final, type = "N"))
  
  grid.text(
    label = paste(
      "Note. Individual measure counts show variable availability;",
      "thus the actual sample sizes per model vary and are shown in tables."
    ),
    x = unit(0.50, "npc"),
    y = unit(0.015, "npc"),
    gp = gpar(cex = 0.65, col = "grey30")
  )
}
```

```{r echo=FALSE, fig.width=10, fig.height=12, dpi=350, dev='jpeg'}
# Save flowchart as JPEG
jpeg(
  filename = paste0(path_to_outputs,"attrition_flowchart.jpg"),
  width = 10,
  height = 12,
  units = "in",
  res = 350,
  quality = 100
)
draw_attrition_flowchart()
dev.off()

# Show flowchart in knitted document
draw_attrition_flowchart()
```

# DESCRIPTIVE STATISTICS TABLE

```{r echo=FALSE}
# Table variables
tab_vars <- c('pain_1day_mnth_18','pain_more3mnths_18','pain_1day_mnth_30','pain_more3mnths_30','sex',baseconf,exp_labs,intc_labs,med_labs,outc_labs)

# Change level labels
desc_df <- alldf %>%
  mutate(
    pain_1day_mnth_18 = factor(sex, levels = c(0,1), labels = c("No","Yes")),
    sex = factor(sex, levels = c(0,1), labels = c("Male","Female")),
    ethnicity = factor(ethnicity, levels = c(0,1), labels = c("White","Minority ethnic")),
    m_pregsmk = factor(m_pregsmk, levels = c(0,1), labels = c("No","Yes")),
    m_homown_0 = factor(m_homown_0, levels = c(0,1), labels = c("Owned","Rented")),
    parent_mhp_1 = factor(parent_mhp_1, levels = c(0,1), labels = c("No","Yes"))
  )

# Function to calculate missingness
missing_col <- function(data, variable, ...) {
  x <- data[[variable]]
  n_miss <- sum(is.na(x))
  p_miss <- sum(is.na(x)) / length(x) * 100
  
  #tibble::tibble(missing = sprintf("%s (%.1f%%)", n_miss, p_miss))
  tibble::tibble(missing = sprintf("%.1f%%", p_miss))
}

# Categories to show in table
rows_shown <- list(
  ethnicity ~ 0,
  m_homown_0 ~ 0
  )

# Create descriptive stats table
tbl_merge(tbls = list(
  
  tbl_summary(
    alldf[, tab_vars],
    type = list(all_dichotomous() ~ "dichotomous"),
    value = rows_shown,
    missing = 'no'
    ) %>%
    add_stat(
      fns = everything() ~ missing_col,
      location = everything() ~ "label"
      ) %>%
    modify_header(missing ~ "**Missing**"),
  
  tbl_summary(
    alldf[, tab_vars], by = 'pain_1day_mnth_18',
    type = list(all_dichotomous() ~ "dichotomous"),
    value = rows_shown,
    missing = 'no'
    ) %>%
    add_p()
  
  ), tab_spanner = paste0('**',c('Overall','Pain in past month (18y)'),'**')) %>%
  
  as_gt()
```


# REGRESSION ESTIMATES

```{r help-func-reg, echo=FALSE}
## Load regression estimates
load(paste0(path_to_outputs,"regression_estimates.rda"))

# Generic table function (creates wide gt table with outcomes as column spanners)
make_gt_table <- function(dat,
                          row_group_var = NULL,
                          title = NULL) {
  
  outcomes <- unique(dat$outcome)
  
  tab_dat <- dat |>
    mutate(
      outcome_id = paste0("out", match(outcome, outcomes)),
      row_label = unname(long_labs[.data[["exposure"]]])
    ) |>
    dplyr::select(
      any_of(row_group_var),
      row_label,
      outcome,
      outcome_id,
      OR_CI,
      p,
      n
    ) |>
    distinct()
  
  wide <- tab_dat |>
    dplyr::select(
      any_of(row_group_var),
      row_label,
      outcome_id,
      OR_CI,
      p,
      n
    ) |>
    pivot_wider(
      names_from = outcome_id,
      values_from = c(OR_CI, p, n),
      names_glue = "{outcome_id}_{.value}"
    )
  
  gt_tab <- wide |>
    gt(
      rowname_col = "row_label",
      groupname_col = row_group_var
    ) |>
    cols_label(
      contains("OR_CI") ~ "OR (95% CI)",
      contains("_p") ~ "p-value",
      contains("_n") ~ "N"
    )
  
  for (i in seq_along(outcomes)) {
    gt_tab <- gt_tab |>
      tab_spanner(
        label = long_labs[outcomes[[i]]],
        columns = starts_with(paste0("out", i, "_"))
      )
  }
  
  if (!is.null(title)) {
    gt_tab <- gt_tab |>
      tab_header(title = title)
  }
  
  gt_tab |>
    tab_style(
      style = cell_text(weight = "bold"),
      locations = cells_column_spanners()
    )
}
```

## Health limitations on later measures

```{r, echo=FALSE}
outcome_order <- c(intc_labs, med_labs, outc_labs)

pop_labs <- c(
  full_sample = "Full sample",
  samp_with_pain = "Sample with pain"
)

results_clean |>
  filter(
    pop %in% names(pop_labs),
    term_type == "exposure",
    exposure %in% exp_labs,
    outcome %in% outcome_order
  ) |>
  mutate(
    pop_lab = recode(pop, !!!pop_labs),
    outcome_group = factor(
      unname(long_labs[outcome]),
      levels = unname(long_labs[outcome_order])
    ),
    term_lab = factor(
      unname(long_labs[exposure]),
      levels = unname(long_labs[exp_labs])
    )
  ) |>
  dplyr::select(
    outcome_group,
    term_lab,
    pop_lab,
    OR_CI,
    p,
    n
  ) |>
  pivot_wider(
    names_from = pop_lab,
    values_from = c(OR_CI, p, n),
    names_glue = "{pop_lab}_{.value}"
  ) |>
  gt(
    groupname_col = "outcome_group",
    rowname_col = "term_lab"
  ) |>
  cols_label(
    contains("OR_CI") ~ "OR (95% CI)",
    contains("_p") ~ "p-value",
    contains("_n") ~ "N"
  ) |>
  tab_spanner(
    label = "Full sample",
    columns = starts_with("Full sample_")
  ) |>
  tab_spanner(
    label = "Sample with pain",
    columns = starts_with("Sample with pain_")
  ) |>
  tab_style(
    style = cell_text(style = "italic", weight = "bold"),
    locations = cells_row_groups()
  ) |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_spanners()
  )
```


## Mental health on social support

### Full sample

```{r, echo=FALSE}
results_clean |>
  filter(
    model_set == "mh_on_support",
    outcome %in% med_labs,
    term %in% intc_labs,
    pop == "full_sample"
  ) |>
  mutate(
    adjustment_lab = paste("Adjusted for", unname(long_labs[adjustments]))
  ) |>
  make_gt_table(row_group_var = "adjustment_lab")
```

### Pain sample

```{r, echo=FALSE}
results_clean |>
  filter(
    model_set == "mh_on_support",
    outcome %in% med_labs,
    term %in% intc_labs,
    pop == "samp_with_pain"
  ) |>
  mutate(
    adjustment_lab = paste("Adjusted for", unname(long_labs[adjustments]))
  ) |>
  make_gt_table(row_group_var = "adjustment_lab")
```


## Mental health on later pain impact

### Full sample

```{r, echo=FALSE}
results_clean |>
  filter(
    model_set == "mh_on_painimpact",
    outcome %in% outc_labs,
    term %in% intc_labs,
    pop == "full_sample"
  ) |>
  mutate(
    adjustment_lab = "Adjusted for equivalent earlier pain impact domain"
  ) |>
  make_gt_table(row_group_var = "adjustment_lab")
```

### Pain sample 

```{r, echo=FALSE}
results_clean |>
  filter(
    model_set == "mh_on_painimpact",
    outcome %in% outc_labs,
    term %in% intc_labs,
    pop == "samp_with_pain"
  ) |>
  mutate(
    adjustment_lab = "Adjusted for equivalent earlier pain impact domain"
  ) |>
  make_gt_table(row_group_var = "adjustment_lab")
```

## Social support on later pain impact

### Full sample

```{r, echo=FALSE}
results_clean |>
  filter(
    model_set == "support_on_painimpact",
    outcome %in% outc_labs,
    term %in% med_labs,
    pop == "full_sample"
  ) |>
  mutate(
    adjustment_lab = case_when(
      adjustments == "no_mh" ~ "Adjusted for equivalent earlier pain impact",
      adjustments == "dep" ~ "Adjusted for equivalent earlier pain impact + depressive symptoms",
      adjustments == "anx" ~ "Adjusted for equivalent earlier pain impact + anxiety symptoms"
    )) |>
  make_gt_table(row_group_var = "adjustment_lab")
```

### Pain sample

```{r, echo=FALSE}
results_clean |>
  filter(
    model_set == "support_on_painimpact",
    outcome %in% outc_labs,
    term %in% med_labs,
    pop == "samp_with_pain"
  ) |>
  mutate(
    adjustment_lab = case_when(
      adjustments == "no_mh" ~ "Adjusted for equivalent earlier pain impact",
      adjustments == "dep" ~ "Adjusted for equivalent earlier pain impact + depressive symptoms",
      adjustments == "anx" ~ "Adjusted for equivalent earlier pain impact + anxiety symptoms"
    )) |>
  make_gt_table(row_group_var = "adjustment_lab")
```

## Plot

```{r regress-plt, echo=FALSE}
# Legend labels
adjustment_labs <- c(
  baseline       = "Baseline confounders",
  domain_hlthlim = "+ Equivalent health limitations (18y)",
  selfc_spl_18   = "+ Health limits daily activities (18y)",
  social_spl_18  = "+ Health limits social activities (18y)",
  work_spl_18    = "+ Health limits work (18y)",
  no_mh          = "+ Equivalent health limitations (18y)",
  dep            = "+ Equivalent health limitations (18y) + Depressive symptoms (21y)",
  anx            = "+ Equivalent health limitations (18y) + Anxiety symptoms (21y)"
)

# Plot data
get_pltdf <- function(dat){
  dat |>
    filter(
      term_type == "exposure",
      model_set %in% c("hlthlim_on",
                       "mh_on_painimpact",
                       "mh_on_support",
                       "support_on_painimpact")
      ) %>%
    mutate(
      exposure = recode(exposure, !!!long_labs),
      outcome = recode(outcome, !!!long_labs),
      adjustments = recode(adjustments, !!!adjustment_labs)
      ) %>%
    mutate(
      exposure = factor(exposure, levels = unique(exposure)),
      outcome = factor(outcome, levels = unique(outcome)),
      adjustments = factor(adjustments, levels = unique(unname(adjustment_labs)))
    )
}

# Plot function
regress_pltit <- function(df){
  
  pd <- position_dodge2(
    width = 0.65,
    preserve = "single",
    padding = 0.15
  )
  
  colours <- c("#999999","#CCBB44", "#D55E00","#4B0092","#0072B2", "#009E73", "#CC79A7", "#56B4E9")
  names(colours) <- unname(adjustment_labs)

  ggplot(df, aes(x = outcome, y = estimate, ymin = (estimate - 1.96 * std.error), ymax = (estimate + 1.96 * std.error), colour = adjustments, group = adjustments)) +
    facet_grid(rows = vars(exposure), switch = "y") + #, scales = "free"
    geom_hline(yintercept = 0, linetype = "dotted") +
    geom_pointrange(
      position = pd,
      linewidth = 0.4,
      size = 0.2
    ) +
    scale_y_continuous(position = "right", 
                       name = "log(OR)\n", 
                       sec.axis = dup_axis(name = "Term\n",  labels = NULL)) +
    scale_color_manual(values = colours) +
    theme_bw() +
    theme(
      legend.position = "bottom",
      legend.location = "plot",
      legend.key.width = unit(15, "pt"),
      legend.spacing.y = unit(1, 'pt'),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 10),
      text = element_text(size = 12), #, family = "Calibri"
      axis.text.x = element_text(angle = 25, hjust = 1),
      axis.ticks.y.left = element_blank(),
      strip.background = element_blank(),
      strip.placement = "outside",
      strip.text = element_text(size = 10),
      strip.text.y.left = element_text(angle = 0, hjust = 0)
    ) +
    labs(x = "\nOutcome", colour = "Adjustment : \n") +
    guides(colour = guide_legend(title.position="top", ncol = 2)
    )
}
```

## Full sample

```{r, echo=FALSE}
regress_all_plt <- regress_pltit(get_pltdf(results_clean[results_clean$pop %in% "full_sample",]))

regress_all_plt

ggsave(plot = regress_all_plt, filename=paste0(path_to_outputs ,"regress_all_plt.jpg"), width = 8, height = 12, dpi = 350)
```

## Pain sample

```{r, echo=FALSE}
regress_wpain_plt <- regress_pltit(get_pltdf(results_clean[results_clean$pop %in% "samp_with_pain",]))

regress_wpain_plt

ggsave(plot = regress_wpain_plt, filename=paste0(path_to_outputs ,"regress_wpain_plt.jpg"), width = 8, height = 12, dpi = 350)
```

## Sex effects

```{r, echo=FALSE}
outcome_order <- c(exp_labs, intc_labs, med_labs, outc_labs)

results_clean |>
  filter(
    pop %in% names(pop_labs),
    model_set == "sex_as_exposure",
    outcome %in% outcome_order
  ) |>
  mutate(
    pop_lab = recode(pop, !!!pop_labs),
    outcome_group = factor(
      unname(long_labs[outcome]),
      levels = unname(long_labs[outcome_order])
    ),
    term_lab = case_when(term == "sex" ~ "Sex")
  ) |>
  dplyr::select(
    outcome_group,
    term_lab,
    pop_lab,
    OR_CI,
    p,
    n
  ) |>
  pivot_wider(
    names_from = pop_lab,
    values_from = c(OR_CI, p, n),
    names_glue = "{pop_lab}_{.value}"
  ) |>
  gt(
    groupname_col = "outcome_group",
    rowname_col = "term_lab"
  ) |>
  cols_label(
    contains("OR_CI") ~ "OR (95% CI)",
    contains("_p") ~ "p-value",
    contains("_n") ~ "N"
  ) |>
  tab_spanner(
    label = "Full sample",
    columns = starts_with("Full sample_")
  ) |>
  tab_spanner(
    label = "Sample with pain",
    columns = starts_with("Sample with pain_")
  ) |>
  tab_style(
    style = cell_text(style = "italic", weight = "bold"),
    locations = cells_row_groups()
  ) |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_spanners()
  )
```

## Sex interaction tables

```{r help-func-sexint, echo=FALSE}
# Function to fit one model and extract interaction + stratified effects
get_sex_int_results <- function(dat, pain_exp, outc, base = baseconf) {
  
  form <- reformulate(
    termlabels = c(paste0("sex", "*", pain_exp), base),
    response = outc
  )
  
  mod <- glm(
    formula = form,
    family = binomial(link = "logit"),
    data = dat
  )

  # Interaction term
  
  tidy_mod <- broom::tidy(mod)
  
  int_term <- tidy_mod |>
    filter(str_detect(term, ":")) |>
    pull(term)

  int_res <- tidy_mod |>
    filter(term == int_term) |>
    transmute(
      pain_exp = pain_exp,
      outcome = outc,
      estimate_id = "interaction",
      estimate_label = "Sex:Health limitation interaction",
      term = term,
      OR = exp(estimate),
      conf.low = exp(estimate - 1.96 * std.error),
      conf.high = exp(estimate + 1.96 * std.error),
      p.value = p.value
    )
  
  # Sex-stratified pain effects
  difference1 <- pain_exp
  difference2 <- paste(pain_exp, int_term, sep = "+")
  
  effx0 <- lincom(mod, difference1, eform = T)
  effx1 <- lincom(mod, difference2, eform = T)
  
  strat_res <- bind_rows(
    as_tibble(effx0) |>
      mutate(
        pain_exp = pain_exp,
        outcome = outc,
        estimate_id = "strat1",
        estimate_label = "Health limitation effect: Male",
        term = difference1
        ),
    
    as_tibble(effx1) |>
      mutate(
        pain_exp = pain_exp,
        outcome = outc,
        estimate_id = "strat2",
        estimate_label = "Health limitation effect: Female",
        term = difference2
        )
    ) |>
    rename(
      OR = Estimate,
      conf.low = `2.5 %`,
      conf.high = `97.5 %`,
      p.value = `Pr(>Chisq)`
      ) |>
    dplyr::select(-Chisq)
  
  bind_rows(int_res, strat_res) |>
    mutate(
      OR_CI = sprintf("%.2f (%.2f, %.2f)", OR, conf.low, conf.high),
      p = case_when(
        p.value < 0.001 ~ "<0.001",
        TRUE ~ sprintf("%.3f", p.value)
        )
    )
}

# Function to run across all pain exposures and later measures
run_sex_int <- function(df, base = baseconf){
  tidyr::expand_grid(
    pain_exp = exp_labs,
    outcome = c(intc_labs, med_labs, outc_labs)
    ) |>
    mutate(
      res = map2(
        pain_exp,
        outcome,
        ~ get_sex_int_results(
          dat = df,
          pain_exp = .x,
          outc = .y,
          base = base
          )
        )
      ) |>
    dplyr::select(-pain_exp, -outcome) |>
    unnest(res) |>
    mutate(
      pain_exp_lab = factor(
        unname(long_labs[pain_exp]),
        levels = unname(long_labs[exp_labs])
        ),
      outcome_lab = factor(
        unname(long_labs[outcome]),
        levels = unname(long_labs[c(intc_labs, med_labs, outc_labs)])
        )
    )
}

# Function to produce wide gt table
make_sex_int_table <- function(dat) {
  
  strat_labs <- dat |>
    filter(str_detect(estimate_id, "^strat")) |>
    distinct(estimate_id, estimate_label) |>
    arrange(estimate_id)
  
  wide <- dat |>
    dplyr::select(
      pain_exp_lab,
      outcome_lab,
      estimate_id,
      OR_CI,
      p
    ) |>
    pivot_wider(
      names_from = estimate_id,
      values_from = c(OR_CI, p),
      names_glue = "{estimate_id}_{.value}"
    ) |>
    arrange(pain_exp_lab, outcome_lab)
  
  gt_tab <- wide |>
    gt(
      rowname_col = "outcome_lab",
      groupname_col = "pain_exp_lab"
    ) |>
    cols_label(
      interaction_OR_CI = "OR (95% CI)",
      interaction_p = "p-value"
    ) |>
    tab_spanner(
      label = "Sex:pain impact interaction",
      columns = c(interaction_OR_CI, interaction_p)
    )
  
  # Add labels/spanners for each sex-stratified estimate
  for (i in seq_len(nrow(strat_labs))) {
    
    id <- strat_labs$estimate_id[i]
    lab <- strat_labs$estimate_label[i]
    
    gt_tab <- gt_tab |>
      cols_label(
        !!paste0(id, "_OR_CI") := "OR (95% CI)",
        !!paste0(id, "_p") := "p-value"
      ) |>
      tab_spanner(
        label = lab,
        columns = all_of(c(
          paste0(id, "_OR_CI"),
          paste0(id, "_p")
        ))
      )
  }
  
  gt_tab |>
    tab_style(
      style = cell_text(weight = "bold"),
      locations = cells_column_spanners()
    ) |>
    tab_style(
      style = cell_text(style = "italic", weight = "bold"),
      locations = cells_row_groups()
    )
}
```

### Full sample

#### Adjusted

```{r, echo=FALSE}
run_sex_int(alldf) |>
  make_sex_int_table()
```

#### Unadjusted

```{r, echo=FALSE}
run_sex_int(alldf, base = NULL) |>
  make_sex_int_table()
```

### Pain sample

#### Adjusted

```{r, echo=FALSE}
run_sex_int(df_wpain) |>
  make_sex_int_table()
```

#### Unadjusted

```{r, echo=FALSE}
run_sex_int(df_wpain, base = NULL) |>
  make_sex_int_table()
```


# MEDIATION (GFORMULA) ESTIMATES

```{r help-func-med, echo=FALSE}
## Read in estimates
load(paste0(path_to_outputs, "gformula_estimates.rda"))

## Significant mediation effects
#sig_gform_ests <- gform_ests[gform_ests$pop %in% 'all' & ((gform_ests$LCI < 1 & gform_ests$UCI < 1) | (gform_ests$LCI > 1 & gform_ests$UCI > 1)),]

## Tidy labels
gform_ests <- gform_ests %>%
  mutate(
    exposure = recode(exposure, !!!unlist(long_labs[exp_labs])),
    outcome = recode(outcome, !!!unlist(long_labs[outc_labs])),
    mediator = recode(mediator, !!!unlist(long_labs[med_labs])),
    intconf = recode(intconf, 'none' = 'None', !!!unlist(long_labs[intc_labs]))
    ) %>%
  mutate(
    mediator = factor(mediator, levels = c(long_labs[med_labs])),
    intconf = factor(intconf, levels = c('None', long_labs[intc_labs]))
    )

## Functions to construct g-computation result tables
get_gform_tab <- function(df, model_label) {
  df %>%
    dplyr::filter(intconf %in% model_label) %>%
    dplyr::arrange(exposure, mediator) %>%
    dplyr::select(effect, exposure, mediator, OR_LCI_UCI) %>%
    mutate(Model = model_label) %>%
    pivot_wider(
      names_from = c(exposure, mediator),
      values_from = OR_LCI_UCI,
      values_fill = NA
    )
}

comb_tabs <- function(df1, df2, df3){
  combined_df <- bind_rows(df1, df2, df3)
  combined_df <- combined_df %>% arrange(effect)
  combined_df %>%
    gt(groupname_col = "Model") %>%
    tab_spanner_delim(delim = "_") %>%
    cols_hide(columns = "Model") %>%
    cols_label(effect = "Effect") %>%
    tab_style(style = cell_text(weight = "bold"), 
              locations = list(cells_column_spanners(),
                               cells_column_labels(),
                               cells_body(columns='effect'))) %>%
    tab_style(style = cell_text(weight = "bold", style = "italic"), 
              locations = cells_row_groups())
}
```

### Full sample

```{r, echo=FALSE}
comb_tabs(
  get_gform_tab(gform_ests[gform_ests$pop %in% "all",], 'None'),
  get_gform_tab(gform_ests[gform_ests$pop %in% "all",], 'Higher depressive symptoms (21y)'),
  get_gform_tab(gform_ests[gform_ests$pop %in% "all",], 'Higher anxiety symptoms (21y)')
)
```

### Pain sample

```{r, echo=FALSE}
comb_tabs(
  get_gform_tab(gform_ests[gform_ests$pop %in% "wpain",], 'None'),
  get_gform_tab(gform_ests[gform_ests$pop %in% "wpain",], 'Higher depressive symptoms (21y)'),
  get_gform_tab(gform_ests[gform_ests$pop %in% "wpain",], 'Higher anxiety symptoms (21y)')
)
```

## Plot

```{r gform-plt, echo=FALSE}
## Function to plot gformula results
gform_pltit <- function(df, ymin, ymax, brk){
  pd <- position_dodge(0.6)
  #df$mediator <- factor(df$mediator, levels = long_labs[med_labs], labels=long_labs[med_labs])
  df$outcome <- factor(df$outcome, levels = long_labs[outc_labs], labels=c('Daily activities','Social activities','Work activities'))
  ggplot(df, aes(x=effect, y=logOR, ymin=logLCI, ymax=logUCI, 
                 colour=intconf, shape=intconf, #linetype=sexint,
                 group=intconf)) +
    geom_hline(yintercept = 0, linetype = "dotted") +
    geom_errorbar(lwd=.8, width=.4, position = pd) +
    geom_point(size=2.5, position = pd) +
    facet_grid(rows = vars(mediator), cols = vars(outcome), switch = "y") + #, scales="free"
    #scale_x_discrete(sec.axis = dup_axis(name = "Mediator\n", labels = NULL)) +
    scale_y_continuous(position = "right", limits = c(ymin,ymax), breaks = seq(ymin,ymax,brk),
                       sec.axis = dup_axis(name = "Mediator\n", labels = NULL)) +
    scale_color_manual(values = c("#0072B2", "#4B0092", "#009E73")) +
    #scale_linetype_manual(values=c(1,5)) +
    theme_bw() +
    theme(plot.title = element_text(hjust = 0.5, size = 14),
          legend.position = "bottom", 
          legend.location = "plot",
          legend.text = element_text(size = 13), 
          legend.title = element_text(size = 13),
          text = element_text(size = 14), #, family = "Calibri"
          strip.background = element_blank(),
          strip.placement = "outside",
          strip.text = element_text(size = 12)) +  
    labs(x = "\nEffect", y = "log(OR)\n", title = "Outcome",
         colour = "Intermediate confounder : ", shape = "Intermediate confounder : ") + #linetype = "Sex interaction : "
    guides(colour = guide_legend(title.position="left", order = 1, nrow=1),  
           #linetype = guide_legend(title.position="top", order = 2, nrow=3),
           shape = guide_legend(title.position="left", order = 1, nrow=1))
}
```

### Full sample

```{r, echo=FALSE}
gform_all_plt <- gform_pltit(gform_ests[!gform_ests$effect %in% 'PM' & gform_ests$pop %in% 'all',], ymin=-0.2,ymax=1.2,brk=0.2)

gform_all_plt

ggsave(plot = gform_all_plt, filename=paste0(path_to_outputs,"gform_all_plt.jpg"), width = 12, height = 15, dpi = 350)
```

### Pain sample

```{r, echo=FALSE}
gform_wpain_plt <- gform_pltit(gform_ests[!gform_ests$effect %in% 'PM' & gform_ests$pop %in% 'wpain',], ymin=-0.2,ymax=1.6,brk=0.2)

gform_wpain_plt

ggsave(plot = gform_wpain_plt, filename=paste0(path_to_outputs,"gform_wpain_plt.jpg"), width = 12, height = 15, dpi = 350)
```


# HISTOGRAMS

```{r hist, echo=FALSE}
# Continuous measures
histlabs <- list('selfc_irt_18' = 'Health limits daily activities (18y)',
                 'social_irt_18' = 'Health limits social activities (18y)',
                 'work_irt_18' = 'Health limits work activities (18y)',
                 'mfq_21' = 'Depressive symptoms (21y)',
                 'gad_21' = 'Anxiety symptoms (21y)',
                 'social_integration_sc_25' = 'Wider social network (25y)',
                 'emo_supp_sc_25' = 'Higher emotional support (25y)',
                 'prac_supp_sc_25' = 'Higher practical support (25y)',
                 'covid_inpers_cont_adult' = 'In-person COVID contact (28y)',
                 'covid4_dist_cont_adult' = 'Distant COVID contact (28y)',
                 'o_daily_acts_30' = 'Pain impacts daily activities, no added zeroes (30y)', 
                 'o_social_30' = 'Pain impacts social activities, no added zeroes (30y)', 
                 'o_work_30' = 'Pain impacts work activities, no added zeroes (30y)',
                 'o_daily_acts_30_zeros' = 'Pain impacts daily activities (30y)', 
                 'o_social_30_zeros' = 'Pain impacts social activities (30y)', 
                 'o_work_30_zeros' = 'Pain impacts work activities (30y)'
)

# Histogram function
hist_pltit <- function(x, dat){
  compdat <- dat[!is.na(dat[,x]),]
  ggplot(compdat, aes(x = compdat[,x])) +
    geom_density(color = "blue", linewidth = 1) +
    geom_histogram(aes(y = after_stat(density)), bins = 30, 
                   fill = "lightblue", color = "white", alpha = 0.9) +
    theme_minimal() +
    theme(text = element_text(size = 6)) + #, family = "Calibri"
    labs(x = histlabs[x], y = "Density/Frequency")
}
hists_all <- lapply(names(histlabs), hist_pltit, alldf)
hists_wpain <- lapply(names(histlabs), hist_pltit, df_wpain)
```

## Full sample

```{r, echo=FALSE}
hists_all <- ggarrange(plotlist=hists_all, ncol=4, nrow=4)

hists_all

ggsave(plot = hists_all, filename=paste0(path_to_outputs,"hist_all_plt.jpg"), width = 10, height = 10, dpi = 350)
```

## Pain sample

```{r, echo=FALSE}
hists_wpain <- ggarrange(plotlist=hists_wpain, ncol=4, nrow=4)

hists_wpain

ggsave(plot = hists_wpain, filename=paste0(path_to_outputs,"hist_wpain_plt.jpg"), width = 10, height = 10, dpi = 350)
```


# CORRELATION MATRICES

## Analysis variables

```{r, echo=FALSE}
get_analys_corr <- function(dat){
  vars <- tab_vars[!tab_vars %in% c('pain_more3mnths_18','pain_more3mnths_30')]
  model.matrix(~0+., data=dat[,vars]) %>% 
    cor(use="pairwise.complete.obs") %>%
    ggcorrplot(show.diag=FALSE, type="lower", 
               lab=TRUE, lab_size=2, tl.cex=10,
               legend.title = "Correlation coefficient") +
    theme(legend.position = "bottom")
}
```

### Full sample

```{r, echo=FALSE, warning=FALSE}
get_analys_corr(alldf)

ggsave(plot = get_analys_corr(alldf), filename=paste0(path_to_outputs,"corrmat_analys_all.jpg"), width = 8, height = 8, dpi = 350)
```

### Pain sample

```{r, echo=FALSE, warning=FALSE}
get_analys_corr(df_wpain)

ggsave(plot = get_analys_corr(df_wpain), filename=paste0(path_to_outputs,"corrmat_analys_wpain.jpg"), width = 8, height = 8, dpi = 350)
```

## IRT variables

```{r, echo=FALSE}
# Items used in latent constructs of early pain impact and social support
irt_vars <- c('sf36_sc_modacts_18' = 'Current health limits moderate activities', 
              'sf36_sc_groceries_18' = 'Current health limits lifting or carrying groceries', 
              'sf36_sc_onestair_18' = 'Current health limits climbing one flight of stairs', 
              'sf36_sc_kneel_18' = 'Current health limits bending, kneeling or stooping', 
              'sf36_sc_walkhlfmile_18' = 'Current health limits walking half a mile',
              'sf36_sc_walk100m_18' = 'Current health limits walking one hundred metres', 
              'sf36_sc_bathdress_18' = 'Current health limits bathing or dressing yourself',
              'sf36_w_cuttime_18' = 'Cut down on amount of time spent on work or other activities as a result of physical health in past 4 weeks', 
              'sf36_w_accomp_18' = 'Accomplished less than would like as a result of physical health in past 4 weeks', 
              'sf36_w_limitkind_18' = 'Limited in kind of work or other activities as a result of physical health in past 4 weeks', 
              'sf36_w_difficulty_18' = 'Had difficulty performing work or other activities as a result of physical health in past 4 weeks',
              'sf36_s_amount_18' = 'Had problem with work or regular activities as a result of emotional respondent had problems in past 4 weeks: cut down on amount of time spent on work or other activities', 
              'sf36_s_accomp_18' = 'Accomplished less than would like due to emotional problems', 
              'sf36_s_lesscareful_18' = 'Did work or activities less carefully than usual due to emotional problems',
              'sf36_s_extent_soc_18' = 'Extent physical health or emotional problems interfered with normal social activities with family, friends, neighbours, or groups in past 4 weeks', 
              'sf36_s_amount_soc_18' = 'Amount of time respondents physical health or emotional problems interfered with social activities in past 4 weeks'
)

get_irt_corr <- function(dat){
  model.matrix(~0+., data=dat[,names(irt_vars)]) %>% 
  cor(use="pairwise.complete.obs") %>% 
  ggcorrplot(show.diag=FALSE, type="lower", 
             lab=TRUE, lab_size=2, tl.cex=10, 
             legend.title = "Correlation coefficient") +
  theme(legend.position = "bottom")
}
```

### Full sample

```{r, echo=FALSE, warning=FALSE}
get_irt_corr(alldf)

ggsave(plot = get_irt_corr(alldf), filename=paste0(path_to_outputs,"corrmat_irt_all.jpg"), width = 8, height = 8, dpi = 350)
```

### Pain sample

```{r, echo=FALSE, warning=FALSE}
get_irt_corr(df_wpain)

ggsave(plot = get_irt_corr(df_wpain), filename=paste0(path_to_outputs,"corrmat_irt_wpain.jpg"), width = 8, height = 8, dpi = 350)
```


# PREDICTORS OF MISSINGNESS

## Univariable

```{r, echo=FALSE, warning=FALSE}
cc_vars <- unique(c(outc_labs, exp_labs, intc_labs, med_labs, 'sex', baseconf))
alldf$completecase <- as.integer(complete.cases(alldf[, cc_vars]))
table(alldf$completecase)
prop.table(table(alldf$completecase))

tbl_uvregression(alldf[,c('completecase',cc_vars)], 
                 y=completecase, 
                 method=glm, 
                 method.args = list(family = binomial(link = "logit")),
                 exponentiate=T) %>%
  as_gt()
```

## Multivariable

```{r, echo=FALSE, warning=FALSE}
# Function to fit models
fit_multvmiss <- function(expos, outc){
  form <- formula(paste('completecase ~',
                        paste(c(outc, expos, med_labs, 'sex', 'm_homown_0'), collapse=' + ')))
  glm(formula=form, 
      data=alldf,
      family=binomial(link = "logit"))
}

# Fit models
mutlvmiss_mods <- list(
  fit_multvmiss(exp_labs[1],outc_labs[1]),
  fit_multvmiss(exp_labs[2],outc_labs[2]),
  fit_multvmiss(exp_labs[3],outc_labs[3])
)

# Create tables
mutlvmiss_tabs <- lapply(mutlvmiss_mods, function(mod) tbl_regression(mod, exponentiate=T))

# Check Ns
check_vars <- function(i) {
  
  vars <- c(exp_labs[i], outc_labs[i], med_labs, "sex", "m_homown_0")
  cc <- complete.cases(alldf[, vars])
  
  tibble(
    domain = c("Daily", "Social", "Work")[i],
    exposure = exp_labs[i],
    outcome = outc_labs[i],
    n = sum(cc),
    completecase_0 = sum(alldf$completecase[cc] == 0, na.rm = TRUE),
    completecase_1 = sum(alldf$completecase[cc] == 1, na.rm = TRUE)
  )
}
cc_check <- map_dfr(1:3, check_vars)
cc_check$prop <- cc_check$completecase_0/cc_check$n

# Merge tables
tbl_merge(mutlvmiss_tabs,
          tab_spanner = paste0('**',c("Daily (n = 712)",
                                      "Social (n = 703)",
                                      "Work (n = 706)"),'**')) %>%
  modify_table_body(~.x %>% dplyr::arrange(match(variable, cc_vars))) %>%
  as_gt() %>%
  gt::tab_source_note(
    source_note = gt::md(
      "*Note.* The numbers of incomplete records observed in the above models are as follows: Daily = 159 (22%); Social = 150 (21%); Work = 153 (22%)"
    )
  )
```